Hyperbolicity of Augmented Links in the Thickened Torus

### 2021-09-02 main.tex
finish fixing prop on tori decomp

\tikzset{
every picture/.style={line width=0.8pt, >=stealth,
                       baseline=-3pt,label distance=-3pt},
%%%%%%%%%%  Node styles
emptynode/.style={circle,minimum size=0pt, inner sep=0pt, outer
sep=0},
dotnode/.style={fill=black,circle,minimum size=2.5pt, inner sep=1pt, outer
sep=0},
small_dotnode/.style={fill=black,circle,minimum size=2pt, inner sep=0pt, outer
sep=0},
morphism/.style={fill=white,circle,draw,thin, inner sep=1pt, minimum size=15pt,
                 scale=0.8},
small_morphism/.style={fill=white,circle,draw,thin,inner sep=1pt,
                       minimum size=10pt, scale=0.8},
ellipse_morphism/.style args={#1}{fill=white,circle,draw,thin,inner sep=1pt,
                       minimum size=5pt, scale=0.8,
												ellipse, draw, rotate=#1},
%note that ellipse stretches based on the text inside, so put \;\;\; in label
coupon/.style={draw,thin, inner sep=1pt, minimum size=18pt,scale=0.8},
semi_morphism/.style args={#1,#2}{
                  fill=white,semicircle,draw,thin, inner sep=1pt, scale=0.8,
                  shape border rotate=#1,
                  label={#1-90:#2}},
%%can only rotate semi_morphisms by right angles tho
%%%% different line styles:
regular/.style={densely dashed}, %% for the regular color, i.e. sum d_i
edge/.style={very thick, draw=green, text=black},
overline/.style={preaction={draw,line width=2mm,white,-}},
thin_overline/.style={preaction={draw,line width=#1 mm,white,-}},
thin_overline/.default=2,
thick_overline/.style={preaction={draw,line width=3mm,white,-}},
really_thick/.style={line width=3mm, gray},
%drinfeld center/.style={>=stealth,green!60!black, double
%distance=1pt,text=black},
boundary/.style={thick,  draw=blue, text=black},
%arrow_decoration={markings, mark=at position 0.5 with {\arrow{>}}}
ribbon/.style={line width=1.5mm, postaction={draw,line width=1mm,white}},
ribbon_u/.style args={#1,#2}{line width=#1mm, postaction={draw,line width=#2mm,white}},
%use line width=0.4pt for thin lines to point to things
%%%%%%% Fill styles %%%%%%%%%%%%%%%
cell/.style={fill=black!10},
subgraph/.style={fill=black!30},
%%%%%%% Mid-path arrows
midarrow/.style={postaction={decorate},
                 decoration={
                    markings,% switch on markings
                    mark=at position #1 with {\arrow{>}},
                 }},
midarrow/.default=0.5,
%%%%% Mid-path arrow but reverse
midarrow_rev/.style={postaction={decorate},
                 decoration={
                    markings,% switch on markings
                    mark=at position #1 with {\arrow{<}},
                 }},
midarrow_rev/.default=0.5,
%%%%% for the flowchart; need align=center to allow multiline in node
block/.style={rectangle, rounded corners, text centered, draw=black, align=center}
}

@@

\begin{definition}
Let $G$ be a graph on the torus.
Let $v$ be a vertex and $e,e'$ be distinct edges that meet $v$.
A \emph{left (resp. right) bow-tie modification to $v,e,e'$}
is the process of removing $v,e,e'$ and adding in a ``bow-tie''
as in Figure \ref{TODO} (a) (resp. (b)).
We call the TODO \emph{long} edges, the TODO \emph{short} edges,
and TODO \emph{diagonal} edges,
and we call the new triangular faces the \emph{bow-tie faces}.
TODO in figure caption, left bow-tie modification so-called because
the triangular face appears to the left of the long edges;
also note that left/right conincide with Figure \ref{f:right_left_aug}

@@

\begin{define}
We say a twist region is \emph{right-augmented} if, when both strands are
(locally) oriented so that they cross the augmentation disk in the same
direction, the crossing is a positive right-handed half-twist.
We say a twist is \emph{left-augmented} if it is not right-augmented.
See Figure \ref{f:right_left_aug}.
\end{define}

@@

We call the resulting graph the \emph{top bow-tie graph of $L$},
denoted by $\Gamma_T(L)$.
If we had oriented the edges of $D'$ the other way,
and subsequently performed the same operations,
we obtain another graph,
which we call the \emph{bottom bow-tie graph of $L$},
denoted by $\Gamma_B(L)$.
%\hfill $\triangle$
\end{definition}

@@

Note that the non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
are naturally identified with the faces of $D'$
(as the bow-tie modification procedure does not remove faces).

@@

\begin{proof}
%As mentioned before, we will be combining
%Menasco's method using crossing edges at each crossing
%and Lackenby's ``cut-slice-flatten'' method
%on augmentation sites.

%We give a description of the topological operations
%that give the torihedral decomposition;
%this will justify the 
%more concise description purely in terms of link diagrams
%which we present in Remark \ref{r:tori-decomp-graph}.

We will begin by assuming that $L$ has no half twists.
Let $L = K \cup C$, with $C$ being the collection of crossing circles.
%Arrange the link diagram of $L$ in the following way:
Arrange $L$ in the following way:
place the circle components in $C$ perpendicular to
the projection plane $\torus \times \{0\}$,
and leave the remaining part of the link $K \subseteq L$
lying in the projection plane (except at crossings of $K$).
Thus, the projection of $L$ onto the projection plane
will be a diagram $D(K)$ of $K$
together with line segments corresponding to crossing circles.
%(We demand that $D(K)$ be alternating and twist-reduced.)
As discussed before, we may remove full twists (i.e. pairs of bigons)
from the twist regions of $K$ that are augmented in $L$,
and since $L$ is assumed to have no half twists,
the two edges of $D(K)$ that go through a crossing circle
do not meet (see Figure \ref{fig:Augmentations} C).
From now on, we will take $K$ to be this modified link
(with full twists removed).

We now place a \emph{crossing edge} at each crossing of $K$,
connecting the top and bottom strands at the crossing
(see \figref{f:crossing-edges}).
%(see Figure \ref{fig:crossingArc} (a)).
%so that for each crossing edge,
%one end of the edge lies on a bottom strand while the other
%end lies on a top strand as in Figure \ref{fig:crossingArc} (a).

@@

Next we construct the graph that will define the torihedra.
We view the link from the point at infinity from the top end
($\torus \times \{1\}$) of the thickened torus.
At each crossing of $K$,
push the top strand towards the bottom strand,
splitting the crossing edge into two
identical edges and spreading them apart as in
\figref{f:crossing-edges}.
%Figure \ref{fig:crossingArc}.
% (b).
%We push the link
%components to infinity and stretch the crossing edge so that we have flattened
%the link onto $\torus \times \{0\}$ except for the crossing circles,
%which remains perpendicular to the projection plane.

@@

\begin{figure}[ht]
\input{fig-cut-slice-flatten.tikz}
\caption{Cut-slice-flatten}
\label{f:cut-slice-flatten}
\end{figure}

@@

The crossing edges and edges from spanning disks of crossing circles
form the graph of the top ideal torihedron.
It is not hard to see that this graph is $\Gamma_T(L)$.
We repeat similar steps for the bottom half of $\torus \times I$,
$\torus \times (-1,0]$
(note we should be pushing the bottom strands up towards the top strand).
It is also easy to see that this graph is $\Gamma_B(L)$
(from the same perspective, not from the perspective of the bottom end
$\torus \times \{-1\}$).
Thus we get two ideal torihedra.
%The graph of each will come from
%crossing edges and edges from spanning disks of crossing circles.

We obtain the complement of $L$ by gluing the two torihedra with the gluing
information given by identifying crossing edges and triangles of the bow-tie.
As observed before, the non-bow-tie faces of $\Gamma_T(L),\Gamma_B(L)$
naturally pair up, and we glue them accordingly
(there is a ``$2\pi/n$'' twist when gluing these faces,
where $n$ is the number of sides of each face as in Figure
\ref{fig:top-bottom} clockwise or counterclockwise).
The bow-tie triangular faces are glued up according to
\figref{fig:falGluings} (a).
%We glue the faces of the torihedra which do not correspond to a bow-tie with a
%$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
%\ref{fig:top-bottom} clockwise or counterclockwise.

Now, if $L$ has half-twists,
we apply the constructions above to $L'$,
which is the link obtained from $L$ by removing all half-twists
(replacing them with parallel strands).
The complement of $L$ is again obtained by
gluing the torihedra together all the same,
except that at the bow-ties coming from twist regions with a half-twist,
they are glued as in Figure \ref{fig:falGluings} (b).
%we decompose the complement of the link the same way
%(as if there are no half twists)
%but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
%Finally,

%%For future reference, we will denote the graph for the top and bottom
%%torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
%%where both graphs are viewed from the cone point of the top torihedron
%%$\torus \times \{1\}$.
%%Note that if $L = K$ is the non-augmented link,
%%$\Gamma_T(L)$ is simply the link projection of $K$,
%%and in fact $\Gamma_T(K) = \Gamma_B(K)$.
\end{proof}

>>>>

\tikzset{
every picture/.style={line width=0.8pt, >=stealth,
                       baseline=-3pt,label distance=-3pt},
%%%%%%%%%%  Node styles
emptynode/.style={circle,minimum size=0pt, inner sep=0pt, outer
sep=0},
dotnode/.style={fill=black,circle,minimum size=2.5pt, inner sep=1pt, outer
sep=0},
small_dotnode/.style={fill=black,circle,minimum size=2pt, inner sep=0pt, outer
sep=0},
morphism/.style={fill=white,circle,draw,thin, inner sep=1pt, minimum size=15pt,
                 scale=0.8},
small_morphism/.style={fill=white,circle,draw,thin,inner sep=1pt,
                       minimum size=10pt, scale=0.8},
ellipse_morphism/.style args={#1}{fill=white,circle,draw,thin,inner sep=1pt,
                       minimum size=5pt, scale=0.8,
												ellipse, draw, rotate=#1},
%note that ellipse stretches based on the text inside, so put \;\;\; in label
coupon/.style={draw,thin, inner sep=1pt, minimum size=18pt,scale=0.8},
semi_morphism/.style args={#1,#2}{
                  fill=white,semicircle,draw,thin, inner sep=1pt, scale=0.8,
                  shape border rotate=#1,
                  label={#1-90:#2}},
%%can only rotate semi_morphisms by right angles tho
%%%% different line styles:
regular/.style={densely dashed}, %% for the regular color, i.e. sum d_i
edge/.style={very thick, draw=green, text=black},
overline/.style={preaction={draw,line width=2mm,white,-}},
thin_overline/.style={preaction={draw,line width=#1 mm,white,-}},
thin_overline/.default=2,
thick_overline/.style={preaction={draw,line width=3mm,white,-}},
really_thick/.style={line width=3mm, gray},
%drinfeld center/.style={>=stealth,green!60!black, double
%distance=1pt,text=black},
boundary/.style={thick,  draw=blue, text=black},
%arrow_decoration={markings, mark=at position 0.5 with {\arrow{>}}}
ribbon/.style={line width=1.5mm, postaction={draw,line width=1mm,white}},
ribbon_u/.style args={#1,#2}{line width=#1mm, postaction={draw,line width=#2mm,white}},
%use line width=0.4pt for thin lines to point to things
%%%%%%% Fill styles %%%%%%%%%%%%%%%
cell/.style={fill=black!10},
subgraph/.style={fill=black!30},
%%%%%%% Mid-path arrows
midarrow/.style={postaction={decorate},
                 decoration={
                    markings,% switch on markings
                    mark=at position #1 with {\arrow{>}},
                 }},
midarrow/.default=0.5,
%%%%% Mid-path arrow but reverse
midarrow_rev/.style={postaction={decorate},
                 decoration={
                    markings,% switch on markings
                    mark=at position #1 with {\arrow{<}},
                 }},
midarrow_rev/.default=0.5,
%%%%% Mid-path arrow but thin
midarrow_thin/.style={postaction={decorate},
                 decoration={
                    markings,% switch on markings
                    mark=at position #1 with {\arrow{Classical TikZ
											Rightarrow[length=2pt]}},
                 }},
midarrow_thin/.default=0.5,
%%%%% for the flowchart; need align=center to allow multiline in node
block/.style={rectangle, rounded corners, text centered, draw=black, align=center}
}

@@

\begin{definition}
Let $G$ be a graph on the torus.
Let $v$ be a vertex and $e,e'$ be distinct edges that meet $v$.
A \emph{left (resp. right) bow-tie modification to $v,e,e'$}
is the process of removing $v,e,e'$ and adding in
a pair of triangular faces, which we refer to as a ``bow-tie''
(see \figref{f:bow-tie-modification}).
%as in Figure \ref{TODO} (a) (resp. (b)).
The edges of the bow-tie are of three types;
\emph{diagonal} edges, which do not touch $v$,
\emph{long} edges, which are ``parallel'' to the original edges $e,e'$,
and \emph{short} edges, which connect $v$ to the two new vertices.
We call the new triangular faces the \emph{bow-tie faces}.

@@

\begin{define}
We say a twist region is \emph{right-augmented} if, when both strands are
(locally) oriented so that they cross the augmentation disk in the same
direction, the crossing is a right-handed half-twist.
We say a twist is \emph{left-augmented} if it is not right-augmented.
(See \figref{f:bow-tie-modification}).
\end{define}

@@

We call the resulting graph the \emph{top bow-tie graph of $L$},
denoted by $\Gamma_T(L)$.
If we had oriented the edges of $D'$ the other way,
and subsequently performed the same operations,
we obtain another graph,
which we call the \emph{bottom bow-tie graph of $L$},
denoted by $\Gamma_B(L)$.
%\hfill $\triangle$

Note that the non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
are naturally identified with the faces of $D'$
(as the bow-tie modification procedure does not remove faces).
\end{definition}

@@

@@

\begin{proof}
As mentioned before, we will be combining
Menasco's method using crossing edges at each crossing
and Lackenby's ``cut-slice-flatten'' method
on augmentation sites.

%We will begin by assuming that $L$ has no half twists.
Let $L = K \cup C$, with $C$ being the collection of crossing circles.
Arrange $L$ in the following way:
place the circle components in $C$ perpendicular to
the projection plane $\torus \times \{0\}$,
and leave the remaining part of the link $K \subseteq L$
lying in the projection plane (except at crossings of $K$).
Thus, the projection of $L$ onto the projection plane
will be a diagram $D(K)$ of $K$
together with line segments corresponding to crossing circles.
%(We demand that $D(K)$ be alternating and twist-reduced.)
%As discussed before, we may remove full twists (i.e. pairs of bigons)
%from the twist regions of $K$ that are augmented in $L$,
%and since $L$ is assumed to have no half twists,
%the two edges of $D(K)$ that go through a crossing circle
%do not meet (see \figref{fig:Augmentations} C).
%From now on, we will take $K$ to be this modified link
%(with full twists removed).

We now place a \emph{crossing edge} at each crossing of $K$,
connecting the top and bottom strands at the crossing
(see \figref{f:crossing-edges}).
We also three horizontal edges for each crossing circle
(see \figref{f:cut-slice-flatten}, leftmost diagram).
%(see Figure \ref{fig:crossingArc} (a)).
%so that for each crossing edge,
%one end of the edge lies on a bottom strand while the other
%end lies on a top strand as in Figure \ref{fig:crossingArc} (a).

@@

%Next we construct the graph that will define the torihedra.
View the link from the point at infinity from the top end
($\torus \times \{1\}$) of the thickened torus.
At each crossing of $K$,
push the top strand towards the bottom strand,
splitting the crossing edge into two
identical edges and spreading them apart as in
\figref{f:crossing-edges}.
Note that after this operation, the link (which is no longer a link)
for both top and bottom look the same,
but a crossing edge associated to a crossing
is pushed in different directions;
this contributes to a ``$2\pi/n$'' twist
when gluing back the faces of the top and bottom torihedra.
%Figure \ref{fig:crossingArc}.
% (b).
%We push the link
%components to infinity and stretch the crossing edge so that we have flattened
%the link onto $\torus \times \{0\}$ except for the crossing circles,
%which remains perpendicular to the projection plane.

@@

\begin{figure}[ht]
\input{fig-cut-slice-flatten.tikz}
\caption{Cut-slice-flatten;
the even and odd refer to the number of crossings
in that twist region
(we only draw one crossing in the first diagram);
the top and bottom graphs are glued back,
gray face to gray face, white face to white face;
note that the graph does not depend on the
parity of the number of crossings, but the gluing is different}
\label{f:cut-slice-flatten}
\end{figure}

Finally, we shrink all remaining segments of the link $L$
to ideal vertices.
It is easy to see that the top and bottom graphs
are exactly $\Gamma_T(L)$ and $\Gamma_B(L)$ from
\defref{d:tori-decomp-graph}.
To recover the link complement,
we glue bow-tie to bow-tie as described in \figref{f:cut-slice-flatten},
and glue each non-bow-tie face to its natural counterpart
(see \defref{d:tori-decomp-graph}),
with a ``$2\pi/n$'' twist as discussed before.

@@

%%The crossing edges and edges from spanning disks of crossing circles
%%form the graph of the top ideal torihedron.
%%It is not hard to see that this graph is $\Gamma_T(L)$.
%%We repeat similar steps for the bottom half of $\torus \times I$,
%%$\torus \times (-1,0]$
%%(note we should be pushing the bottom strands up towards the top strand).
%%It is also easy to see that this graph is $\Gamma_B(L)$
%%(from the same perspective, not from the perspective of the bottom end
%%$\torus \times \{-1\}$).
%%Thus we get two ideal torihedra.
%%%The graph of each will come from
%%%crossing edges and edges from spanning disks of crossing circles.
%%
%%
%%We obtain the complement of $L$ by gluing the two torihedra with the gluing
%%information given by identifying crossing edges and triangles of the bow-tie.
%%As observed before, the non-bow-tie faces of $\Gamma_T(L),\Gamma_B(L)$
%%naturally pair up, and we glue them accordingly
%%(there is a ``$2\pi/n$'' twist when gluing these faces,
%%where $n$ is the number of sides of each face as in Figure
%%\ref{fig:top-bottom} clockwise or counterclockwise).
%%The bow-tie triangular faces are glued up according to
%%\figref{fig:falGluings} (a).
%%%We glue the faces of the torihedra which do not correspond to a bow-tie with a
%%%$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
%%%\ref{fig:top-bottom} clockwise or counterclockwise.
%%
%%
%%Now, if $L$ has half-twists,
%%we apply the constructions above to $L'$,
%%which is the link obtained from $L$ by removing all half-twists
%%(replacing them with parallel strands).
%%The complement of $L$ is again obtained by
%%gluing the torihedra together all the same,
%%except that at the bow-ties coming from twist regions with a half-twist,
%%they are glued as in Figure \ref{fig:falGluings} (b).
%%%we decompose the complement of the link the same way
%%%(as if there are no half twists)
%%%but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
%%%Finally,
%%
%%
%%%%For future reference, we will denote the graph for the top and bottom
%%%%torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
%%%%where both graphs are viewed from the cone point of the top torihedron
%%%%$\torus \times \{1\}$.
%%%%Note that if $L = K$ is the non-augmented link,
%%%%$\Gamma_T(L)$ is simply the link projection of $K$,
%%%%and in fact $\Gamma_T(K) = \Gamma_B(K)$.
\end{proof}
